Bayesian Sparsification of Deep $\cplx$-valued networks -- Extended appendix

### 2020-02-19 paper/appendix.tex
added some conclusion to the appendix

@@

We recap the set up of each experiment on MNIST-like:
\begin{itemize}
  \item staged training, with weight and optimizer state transfer
  \item $40$, $75$, and $40$ epochs for ``dense'', ``sparsify'', and ``fine-tune'' stagers, respectively
  \item ADAM optimizer with learning rate $10^{-3}$ before the $10$-th, and $10^{-4}$
  afterwards
  \item $\ell_2$-norm global gradient clipping at $\tfrac12$
  \item training batches of size $128$ from a fixed randomly subset ($10^4$ images) of the training split
  \item the multiplier of the Kullback-Leibler term in ELBO varies over $
    C \in \{
      \tfrac32 2^{-\tfrac{k}2} \colon k=2, \cdots, 38
    \}
  $
  \item the sparsification threshold $\tau$ is set to $-\tfrac12$
\end{itemize}
Each experiment was performed $5$ times to obtain a small sample of performance-compression
values for each setting of $C$. By reevaluating each setting several times we can account
for randomness in initialization of the uncompressed network at ``dense'', stochasticity of
variational dropout layers, and randomness of batch sequences during SDG, and non-determinism
of computations on GPUs.

@@

\begin{figure}[ht]
  \centering
  \begin{subfigure}[b]{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__ARD__emnist_letters__fft__-0.5.pdf}
  \end{subfigure}%
  \begin{subfigure}[b]{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__ARD__kmnist__fft__-0.5.pdf}
  \end{subfigure} \\ %
  \begin{subfigure}[b]{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__ARD__fashionmnist__fft__-0.5.pdf}
  \end{subfigure}%
  \begin{subfigure}[b]{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__ARD__mnist__fft__-0.5.pdf}
  \end{subfigure}
  \caption{%
    The compression-accuracy trade-off of ARD method for $\real$ and $\cplx$ models using Fourier features.
  }
  \label{fig:appendix__mnist-like__trade-off__ARD__fft}
\end{figure}

\begin{figure}[ht]
  \centering
  \begin{subfigure}[b]{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__VD__emnist_letters__fft__-0.5.pdf}
  \end{subfigure}%
  \begin{subfigure}[b]{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__VD__kmnist__fft__-0.5.pdf}
  \end{subfigure} \\ %
  \begin{subfigure}[b]{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__VD__fashionmnist__fft__-0.5.pdf}
  \end{subfigure}%
  \begin{subfigure}[b]{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__VD__mnist__fft__-0.5.pdf}
  \end{subfigure}
  \caption{%
    The compression-accuracy trade-off of VD method for $\real$ and $\cplx$ models using Fourier features.
  }
  \label{fig:appendix__mnist-like__trade-off__VD__fft}
\end{figure}

\begin{figure}[ht]
  \centering
  \begin{subfigure}[b]{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__ARD__emnist_letters__raw__-0.5.pdf}
  \end{subfigure}%
  \begin{subfigure}[b]{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__ARD__kmnist__raw__-0.5.pdf}
  \end{subfigure} \\%
  \begin{subfigure}[b]{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__ARD__fashionmnist__raw__-0.5.pdf}
  \end{subfigure}%
  \begin{subfigure}[b]{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__ARD__mnist__raw__-0.5.pdf}
  \end{subfigure}
  \caption{%
    The compression-accuracy trade-off of ARD method for $\real$ and $\cplx$ models using raw features.
  }
  \label{fig:appendix__mnist-like__trade-off__ARD__raw}
\end{figure}

\begin{figure}[ht]
  \centering
  \begin{subfigure}[b]{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__VD__emnist_letters__raw__-0.5.pdf}
  \end{subfigure}%
  \begin{subfigure}[b]{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__VD__kmnist__raw__-0.5.pdf}
  \end{subfigure} \\%
  \begin{subfigure}[b]{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__VD__fashionmnist__raw__-0.5.pdf}
  \end{subfigure}%
  \begin{subfigure}[b]{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__VD__mnist__raw__-0.5.pdf}
  \end{subfigure}
  \caption{%
    The compression-accuracy trade-off of VD method for $\real$ and $\cplx$ models using raw features.
  }
  \label{fig:appendix__mnist-like__trade-off__VD__raw}
\end{figure}

\begin{figure}[ht]
  \centering
  \begin{subfigure}[b]{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__cmp__ARD__emnist_letters__fft__-0.5.pdf}
  \end{subfigure}%
  \begin{subfigure}[b]{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__cmp__ARD__kmnist__fft__-0.5.pdf}
  \end{subfigure} \\ %
  \begin{subfigure}[b]{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__cmp__ARD__fashionmnist__fft__-0.5.pdf}
  \end{subfigure}%
  \begin{subfigure}[b]{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__cmp__ARD__mnist__fft__-0.5.pdf}
  \end{subfigure}
  \caption{%
    The compression-accuracy trade-off of ARD method for $2\real$ and $\cplx$ models using Fourier features.
  }
  \label{fig:appendix__cmp__mnist-like__trade-off__ARD__fft}
\end{figure}

\begin{figure}[ht]
  \centering
  \begin{subfigure}[b]{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__cmp__VD__emnist_letters__fft__-0.5.pdf}
  \end{subfigure}%
  \begin{subfigure}[b]{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__cmp__VD__kmnist__fft__-0.5.pdf}
  \end{subfigure} \\ %
  \begin{subfigure}[b]{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__cmp__VD__fashionmnist__fft__-0.5.pdf}
  \end{subfigure}%
  \begin{subfigure}[b]{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__cmp__VD__mnist__fft__-0.5.pdf}
  \end{subfigure}
  \caption{%
    The compression-accuracy trade-off of VD method for $2\real$ and $\cplx$ models using Fourier features.
  }
  \label{fig:appendix__cmp__mnist-like__trade-off__VD__fft}
\end{figure}

\begin{figure}[ht]
  \centering
  \begin{subfigure}[b]{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__cmp__ARD__emnist_letters__raw__-0.5.pdf}
  \end{subfigure}%
  \begin{subfigure}[b]{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__cmp__ARD__kmnist__raw__-0.5.pdf}
  \end{subfigure} \\%
  \begin{subfigure}[b]{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__cmp__ARD__fashionmnist__raw__-0.5.pdf}
  \end{subfigure}%
  \begin{subfigure}[b]{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__cmp__ARD__mnist__raw__-0.5.pdf}
  \end{subfigure}
  \caption{%
    The compression-accuracy trade-off of ARD method for $\real$ and $\tfrac12\cplx$ models using raw features.
  }
  \label{fig:appendix__cmp__mnist-like__trade-off__ARD__raw}
\end{figure}

\begin{figure}[ht]
  \centering
  \begin{subfigure}[b]{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__cmp__VD__emnist_letters__raw__-0.5.pdf}
  \end{subfigure}%
  \begin{subfigure}[b]{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__cmp__VD__kmnist__raw__-0.5.pdf}
  \end{subfigure} \\%
  \begin{subfigure}[b]{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__cmp__VD__fashionmnist__raw__-0.5.pdf}
  \end{subfigure}%
  \begin{subfigure}[b]{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__cmp__VD__mnist__raw__-0.5.pdf}
  \end{subfigure}
  \caption{%
    The compression-accuracy trade-off of VD method for $\real$ and $\tfrac12\cplx$ models using raw features.
  }
  \label{fig:appendix__cmp__mnist-like__trade-off__VD__raw}
\end{figure}

@@

For the CIFAR10 experiment we reuse the setup of the MNIST-like experiment with the
following exceptions:
\begin{itemize}
  \item we allocate $20$, $40$, and $20$ epochs to each stage
  \item the weight of the KL divergence term varies over a smaller grid $
    C \in \{
      \tfrac32 2^{-\tfrac{k}2} \colon k=7, \cdots, 15
    \}
  $
  \item we use full $50$k training split of the CIFAR10 dataset for training and raw color
  features only
  \item dataset is randomly augmented: every image within a batch of size $128$ is randomly
  cropped and flipped horizontally
\end{itemize}
Random cropping is done by zero-padding each side of a $32\times 32$ image by four pixels
and then a extracting a random $32\times 32$ patch from the $40\times 40$ intermediate image.

>>>>

To supplement the results, reported in the main text (figures \ref{fig:paper__mnist-like__trade-off__VD__fft}
and \ref{fig:paper__mnist-like__trade-off__VD__raw}), we conduct additional experiments
with the same basic setup, but over a finer grid of KL-divergence term coefficients.
%
These experiments lend further evidence in supporting the conclusions, draw in the main
paper, namely that the $\cplx$-valued extension of the $\real$-valued variational dropout
can offer significant compression levels without much loss in performance. At the same
time, the test performance of both $\real$ and $\cplx$ compressed networks benefits from
an extra fine-tuning stage, during which sparsity masks are fixed.

One intriguing observation, is that on MNIST-like images the dense network taking Fourier
features on input, exhibits gradually improving test-split performance. This is in stark
contrast to raw image input, where the performance stays at the one level in the small
compression regime, and then gradually decays at high compression levels. Noteworthy is
the presence of a trough in the pre fine-tuning stage performance in the small compression
regime on figures
\ref{fig:appendix__mnist-like__trade-off__ARD__raw},
\ref{fig:appendix__mnist-like__trade-off__VD__raw},
\ref{fig:appendix__cmp__mnist-like__trade-off__ARD__raw},
and \ref{fig:appendix__cmp__mnist-like__trade-off__VD__raw}, which then slowly disappears
as compression increases.

@@

We recap the set up of each additional experiment on MNIST-like datasets:
\begin{itemize}
  \item staged training, with weight and optimizer state transfer
  \item $40$, $75$, and $40$ epochs for ``dense'', ``sparsify'', and ``fine-tune'' stagers, respectively
  \item ADAM optimizer with learning rate $10^{-3}$ before the $10$-th, and $10^{-4}$
  afterwards
  \item global $\ell_2$-norm gradient clipping set at $\tfrac12$
  \item training batches of size $128$ from a fixed randomly subset ($10^4$ images) of the training split
  \item the multiplier of the Kullback-Leibler term in ELBO varies over $
    C \in \{
      \tfrac32 2^{-\tfrac{k}2} \colon k=2, \cdots, 38
    \}
  $
  \item the sparsification threshold $\tau$ is set to $-\tfrac12$
\end{itemize}
Each experiment was performed $5$ times to obtain a small sample of performance-compression
values for each setting of $C$. By reevaluating each setting several times we can account
for randomness in initialization of the uncompressed network at ``dense'', stochasticity of
variational dropout layers, and randomness of batch sequences during SDG, and non-determinism
of computations on GPUs.

@@

\begin{figure}[ht]
  \centering
  \begin{subfigure}[b]{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__ARD__emnist_letters__fft__-0.5.pdf}
  \end{subfigure}%
  \begin{subfigure}[b]{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__ARD__kmnist__fft__-0.5.pdf}
  \end{subfigure} \\ %
  \begin{subfigure}[b]{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__ARD__fashionmnist__fft__-0.5.pdf}
  \end{subfigure}%
  \begin{subfigure}[b]{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__ARD__mnist__fft__-0.5.pdf}
  \end{subfigure}
  \caption{%
    The trade-off of ARD method for $\real$ and $\cplx$ models using Fourier features.
  }
  \label{fig:appendix__mnist-like__trade-off__ARD__fft}
\end{figure}

\begin{figure}[ht]
  \centering
  \begin{subfigure}[b]{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__VD__emnist_letters__fft__-0.5.pdf}
  \end{subfigure}%
  \begin{subfigure}[b]{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__VD__kmnist__fft__-0.5.pdf}
  \end{subfigure} \\ %
  \begin{subfigure}[b]{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__VD__fashionmnist__fft__-0.5.pdf}
  \end{subfigure}%
  \begin{subfigure}[b]{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__VD__mnist__fft__-0.5.pdf}
  \end{subfigure}
  \caption{%
    The trade-off of VD method for $\real$ and $\cplx$ models using Fourier features.
  }
  \label{fig:appendix__mnist-like__trade-off__VD__fft}
\end{figure}

\begin{figure}[ht]
  \centering
  \begin{subfigure}[b]{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__ARD__emnist_letters__raw__-0.5.pdf}
  \end{subfigure}%
  \begin{subfigure}[b]{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__ARD__kmnist__raw__-0.5.pdf}
  \end{subfigure} \\%
  \begin{subfigure}[b]{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__ARD__fashionmnist__raw__-0.5.pdf}
  \end{subfigure}%
  \begin{subfigure}[b]{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__ARD__mnist__raw__-0.5.pdf}
  \end{subfigure}
  \caption{%
    The trade-off of ARD method for $\real$ and $\cplx$ models using raw features.
  }
  \label{fig:appendix__mnist-like__trade-off__ARD__raw}
\end{figure}

\begin{figure}[ht]
  \centering
  \begin{subfigure}[b]{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__VD__emnist_letters__raw__-0.5.pdf}
  \end{subfigure}%
  \begin{subfigure}[b]{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__VD__kmnist__raw__-0.5.pdf}
  \end{subfigure} \\%
  \begin{subfigure}[b]{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__VD__fashionmnist__raw__-0.5.pdf}
  \end{subfigure}%
  \begin{subfigure}[b]{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__VD__mnist__raw__-0.5.pdf}
  \end{subfigure}
  \caption{%
    The trade-off of VD method for $\real$ and $\cplx$ models using raw features.
  }
  \label{fig:appendix__mnist-like__trade-off__VD__raw}
\end{figure}

\begin{figure}[ht]
  \centering
  \begin{subfigure}[b]{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__cmp__ARD__emnist_letters__fft__-0.5.pdf}
  \end{subfigure}%
  \begin{subfigure}[b]{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__cmp__ARD__kmnist__fft__-0.5.pdf}
  \end{subfigure} \\ %
  \begin{subfigure}[b]{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__cmp__ARD__fashionmnist__fft__-0.5.pdf}
  \end{subfigure}%
  \begin{subfigure}[b]{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__cmp__ARD__mnist__fft__-0.5.pdf}
  \end{subfigure}
  \caption{%
    The trade-off of ARD method for $2\real$ and $\cplx$ models using Fourier features.
  }
  \label{fig:appendix__cmp__mnist-like__trade-off__ARD__fft}
\end{figure}

\begin{figure}[ht]
  \centering
  \begin{subfigure}[b]{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__cmp__VD__emnist_letters__fft__-0.5.pdf}
  \end{subfigure}%
  \begin{subfigure}[b]{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__cmp__VD__kmnist__fft__-0.5.pdf}
  \end{subfigure} \\ %
  \begin{subfigure}[b]{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__cmp__VD__fashionmnist__fft__-0.5.pdf}
  \end{subfigure}%
  \begin{subfigure}[b]{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__cmp__VD__mnist__fft__-0.5.pdf}
  \end{subfigure}
  \caption{%
    The trade-off of VD method for $2\real$ and $\cplx$ models using Fourier features.
  }
  \label{fig:appendix__cmp__mnist-like__trade-off__VD__fft}
\end{figure}

\begin{figure}[ht]
  \centering
  \begin{subfigure}[b]{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__cmp__ARD__emnist_letters__raw__-0.5.pdf}
  \end{subfigure}%
  \begin{subfigure}[b]{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__cmp__ARD__kmnist__raw__-0.5.pdf}
  \end{subfigure} \\%
  \begin{subfigure}[b]{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__cmp__ARD__fashionmnist__raw__-0.5.pdf}
  \end{subfigure}%
  \begin{subfigure}[b]{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__cmp__ARD__mnist__raw__-0.5.pdf}
  \end{subfigure}
  \caption{%
    The trade-off of ARD method for $\real$ and $\tfrac12\cplx$ models using raw features.
  }
  \label{fig:appendix__cmp__mnist-like__trade-off__ARD__raw}
\end{figure}

\begin{figure}[ht]
  \centering
  \begin{subfigure}[b]{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__cmp__VD__emnist_letters__raw__-0.5.pdf}
  \end{subfigure}%
  \begin{subfigure}[b]{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__cmp__VD__kmnist__raw__-0.5.pdf}
  \end{subfigure} \\%
  \begin{subfigure}[b]{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__cmp__VD__fashionmnist__raw__-0.5.pdf}
  \end{subfigure}%
  \begin{subfigure}[b]{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{figure__mnist-like__trade-off/appendix__cmp__VD__mnist__raw__-0.5.pdf}
  \end{subfigure}
  \caption{%
    The trade-off of VD method for $\real$ and $\tfrac12\cplx$ models using raw features.
  }
  \label{fig:appendix__cmp__mnist-like__trade-off__VD__raw}
\end{figure}

\begin{figure}[ht]
  \centering
  \begin{subfigure}[b]{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{../figure__mnist-like__trade-off/legacy__VD__emnist_letters__fft__-0.5.pdf}
  \end{subfigure}%
  \begin{subfigure}[b]{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{../figure__mnist-like__trade-off/legacy__VD__kmnist__fft__-0.5.pdf}
  \end{subfigure} \\%
  \begin{subfigure}[b]{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{../figure__mnist-like__trade-off/legacy__VD__fashionmnist__fft__-0.5.pdf}
  \end{subfigure}%
  \begin{subfigure}[b]{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{../figure__mnist-like__trade-off/legacy__VD__mnist__fft__-0.5.pdf}
  \end{subfigure}
  \caption{%
    The trade-off of VD method for $\real$ and $\cplx$ models using Fourier features (main text).
  }
  \label{fig:paper__mnist-like__trade-off__VD__fft}
\end{figure}

\begin{figure}[ht]
  \centering
  \begin{subfigure}[b]{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{../figure__mnist-like__trade-off/legacy__VD__emnist_letters__raw__-0.5.pdf}
  \end{subfigure}%
  \begin{subfigure}[b]{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{../figure__mnist-like__trade-off/legacy__VD__kmnist__raw__-0.5.pdf}
  \end{subfigure} \\%
  \begin{subfigure}[b]{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{../figure__mnist-like__trade-off/legacy__VD__fashionmnist__raw__-0.5.pdf}
  \end{subfigure}%
  \begin{subfigure}[b]{0.5\textwidth}
    \centering
    \includegraphics[width=\linewidth]{../figure__mnist-like__trade-off/legacy__VD__mnist__raw__-0.5.pdf}
  \end{subfigure}
  \caption{%
    The trade-off of VD method for $\real$ and $\cplx$ models using raw features (main text).
  }
  \label{fig:paper__mnist-like__trade-off__VD__raw}
\end{figure}

@@

In addition to the results reported in the main paper, we conduct additional experiment
on CIFAR10 and VGG16 with a much more slowly annealed learning rate. Similar to MNIST-like
experiments, we start with rate set to $10^{-3}$ and then reduce it by $10$ after the
$10$-the epoch. In summary, for the CIFAR10 experiment we reuse the setup with the following
changes:
\begin{itemize}
  \item we allocate $20$, $40$, and $20$ epochs to each stage
  \item the weight of the KL divergence term varies over a smaller grid $
    C \in \{
      \tfrac32 2^{-\tfrac{k}2} \colon k=7, \cdots, 15
    \}
  $
  \item we use full $50$k training split of the CIFAR10 dataset for training and raw color
  features only
  \item dataset is randomly augmented: every image within a batch of size $128$ is randomly
  cropped and flipped horizontally
\end{itemize}
Random cropping is done by zero-padding each side of a $32\times 32$ image by four pixels
and then a extracting a random $32\times 32$ patch from the $40\times 40$ intermediate image.
